Simulataneous Robot Localization and \\Environment Mapping with \\Simulated Sensor Measurements

### 2018-05-03 paper.tex
Fized figure 7

\texttt{EKFSlammer} stores the robot's and environment's state $x_t$ in a \texttt{VectorXd}. The
perceived position and orientation of the robot, as well as the location of the landmarks in the map, 
can be expressed as 
\begin{equation*}
 x_t = \left[\begin{IEEEeqnarraybox*}[][c]{,c,}
        \vec{s} \\
        \theta \\
        \vec{m}_1x \\
        \vec{m}_1y \\
        \vdots
        \end{IEEEeqnarraybox*}\right],
\end{equation*}
where $\vec{s}$ is the robot's location with respect to the Aruco Marker (the arbitrarily-defined
origin) and $\vec{m}_i$ is the location of the $i$\textsuperscript{th} landmark.

First, to generate the \textit{a priori} estimate, the \texttt{motionModelUpdate()} method is called by 
\texttt{ekfUpdate}. Its parameters are the timestep for the robot and its control parameters, in 
the form of a forward velocity and an angular velocity (i.e. the \texttt{controlIn} struct; see 
\texttt{Utils.h}). The \texttt{motionModelUpdate} calculates the estimated state of the 
robot, given the control input and the known uncertainties of the robot's actuators.

@@

 The vectors represented
in code for measurement updates are the Kinect measurement vector and the gyroscope measurement vector.
The Kinect senses all obstacles in the environment; therefore, its measurement vector for all $i$ obstacles 
is expressed as
\begin{equation*}
 z_{t,K} = \left[\begin{IEEEeqnarraybox*}[][c]{,c,}
           r_1 \\
           \theta_1 \\
           r_2 \\
           \theta_2 \\
           \vdots \\
           r_i \\
           \theta_i
           \end{IEEEeqnarraybox*}\right] + \vec{\epsilon_t},
\end{equation*}
and the gyroscope measurement vector can be expressed as 
\begin{equation*}
 z_{t,g} = \omega_t + \epsilon_t,
\end{equation*}
where $\omega_t$ is the angular velocity of the robot, and $\vec{\epsilon_t}$ and $\epsilon_t$ are the 
normally-distributed noise factors for each sensor.

@@

\begin{figure}[!t]%{0.35\textwidth}
\centering
\includegraphics[width=0.9\linewidth]{Figures/1-actual-predicted-error-x.jpg}
\caption{}
\label{fig:1}
\end{figure}

\begin{figure}[!t]%{0.35\textwidth}
\centering
\includegraphics[width=0.9\linewidth]{Figures/2-actual-predicted-error-y.jpg}
\caption{}
\label{fig:2}
\end{figure}

\begin{figure}[!t]%{0.35\textwidth}
\centering
\includegraphics[width=0.9\linewidth]{Figures/3-actual-predicted-error-theta.jpg}
\caption{}
\label{fig:3}
\end{figure}

>>>>

\texttt{EKFSlammer} stores the robot's and environment's state $x_t$ in a \texttt{VectorXd}. The
perceived position and orientation of the robot, as well as the location of the obstacles in the map, 
can be expressed informally as 
\begin{equation*}
 x_t = \left[\begin{IEEEeqnarraybox*}[][c]{,c,}
        \vec{s} \\
        \theta \\
        \vec{m}_1x \\
        \vec{m}_1y \\
        \vdots
        \end{IEEEeqnarraybox*}\right],
\end{equation*}
where $\vec{s}$ is the robot's location with respect to the Aruco Marker (the arbitrarily-defined
origin) and $\vec{m}_i$ is the location of the $i$\textsuperscript{th} obstacle. The vectors represented
in code for measurement updates are the Kinect measurement vector and the gyroscope measurement vector.
The Kinect senses all obstacles in the environment; therefore, its measurement vector for all $i$ obstacles 
is expressed as
\begin{equation*}
 z_{t,K} = \left[\begin{IEEEeqnarraybox*}[][c]{,c,}
           r_1 \\
           \theta_1 \\
           r_2 \\
           \theta_2 \\
           \vdots \\
           r_i \\
           \theta_i
           \end{IEEEeqnarraybox*}\right] + \vec{\epsilon_t},
\end{equation*}
and the gyroscope measurement vector can be expressed as 
\begin{equation*}
 z_{t,g} = \omega_t + \epsilon_t,
\end{equation*}
where $\omega_t$ is the angular velocity of the robot, and $\vec{\epsilon_t}$ and $\epsilon_t$ are the 
normally-distributed noise factors for each sensor.

First, to generate the \textit{a priori} estimate, the \texttt{motionModelUpdate()} method is called by 
\texttt{ekfUpdate}. Its parameters are the timestep for the robot and its control parameters, in 
the form of a forward velocity and an angular velocity (i.e. the \texttt{controlIn} struct; see 
\texttt{Utils.h}). The \texttt{motionModelUpdate} will recalculate the estimated state of the 
robot, given the control input and given the known uncertainties of the robot's actuators 
(i.e. the robot's wheels, since this robot can only move).

@@

@@

\begin{figure}[!t]%{0.35\textwidth}
\centering
\includegraphics[width=0.9\linewidth]{Figures/1-actual-predicted-error-x.jpg}
\caption{The difference between the actual and predicted values in the $x$-axis.}
\label{fig:1}
\end{figure}

\begin{figure}[!t]%{0.35\textwidth}
\centering
\includegraphics[width=0.9\linewidth]{Figures/2-actual-predicted-error-y.jpg}
\caption{The difference between the actual and predicted values in the $y$-axis.}
\label{fig:2}
\end{figure}

\begin{figure}[!t]%{0.35\textwidth}
\centering
\includegraphics[width=0.9\linewidth]{Figures/3-actual-predicted-error-theta.jpg}
\caption{The difference between the actual and predicted values in $\theta$.}
\label{fig:3}
\end{figure}
